---
title: "CaseStudy01"
author: "Rangaswamy Nagarajan"
date: "June 30, 2017"
output: 
  html_document:
    keep_md: true
---

## Beer

Beer is the world's oldest and most widely consumed alcoholic drink. It is the third most popular drink overall, after water and tea.
This case study is about the analysis of data collected about Beers and Breweries in the United States of America. The data set contains a list of 2,410 US beers and 557 US breweries. 

```{r setup, results='hide'}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
getwd()
setwd("C:/Users/swara/OneDrive/Documents/MSDS/Data Science/CaseStudy/MSDSCaseStudy01/Analysis")
```




```{r, results='hide'}
beers <- read.csv("C:/Users/swara/OneDrive/Documents/MSDS/Data Science/CaseStudy/MSDSCaseStudy01/Data/Beers.csv",header=TRUE)
breweries <- read.csv("C:/Users/swara/OneDrive/Documents/MSDS/Data Science/CaseStudy/MSDSCaseStudy01/Data/Breweries.csv", header=TRUE)

names(beers)[1] <- paste("Beer_Name")
names(breweries)[2] <- paste("Brewery_Name")
```


## Number of breweries in each State.

```{r}
NoOfBreweriesPerState <- data.frame(table(breweries$State))
names(NoOfBreweriesPerState)[1]<-paste("State")
names(NoOfBreweriesPerState)[2]<-paste("Count")
NoOfBreweriesPerState
```

## Merged Beers and Breweries data.
```{r}
beerBrewery<-merge(breweries, beers, by.x="Brew_ID", by.y="Brewery_id", all=TRUE)
head(beerBrewery)
tail(beerBrewery)
```

## Number of NA's in each column.
<!--The below code is used to identify "" and replcae it with NA. 
There were 5 observations with style as "". the below code is used to replace "" with NA --> 
```{r}
beerBrewery$Style<-ifelse(beerBrewery[,9]=="", NA, beerBrewery[,9])
```
<!--The below code is used to count the number of NA is each column. -->
```{r}
na_count <-sapply(beerBrewery, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```


## Median alcohol content for each state.
```{r}
MedABVByState <- aggregate(ABV~State, FUN = median, beerBrewery, na.rm = TRUE)
```

## Bar Chart for Median alcohol content by each state.

```{r MedABVPlot, fig.width=12, fig.height=8}
ggplot(MedABVByState, aes(x=State, y=ABV, fill=ABV))+
  geom_bar(stat="identity")+
  ylab("Median Alcohol Cotent")+
  ggtitle("Medain Alcohol Content by State")+
  theme(plot.title = element_text(hjust = 0.5, size = 12, face="bold"))+
  theme(axis.text = element_text(size = 8, face="bold"))+
  theme(axis.title = element_text(size = 10, face="bold"))+
  scale_fill_gradient(low="#FF9999",high="#000099")

```


## Median international bitterness unit for each state.
```{r}
MedIBUByState <- aggregate(IBU~State, FUN = median, beerBrewery, na.rm = TRUE)
```

## Bar Chart for Median international bitterness unit by each state.
```{r MedIBUPlot, fig.width=12, fig.height=8}
ggplot(MedIBUByState, aes(x=State, y=IBU, fill=IBU))+
  geom_bar(stat="identity")+
  ylab("Median International Bitterness Unit")+
  ggtitle("Medain International Bitterness Unit by State")+
  theme(plot.title = element_text(hjust = 0.5, size = 12, face="bold"))+
  theme(axis.text = element_text(size = 8, face="bold"))+
  theme(axis.title = element_text(size = 10, face="bold"))+
  scale_fill_gradient(low="#FF9999",high="#000099")
```

## State that has the most alcoholic beer.
```{r}
maxAlcoholRow<-head(beerBrewery[order(-beerBrewery$ABV),],1)
maxAlcoholState<-as.character(maxAlcoholRow$State)
maxAlcoholState
```


## State that has the most bitter beer.
```{r}
maxBitterRow<-head(beerBrewery[order(-beerBrewery$IBU),],1)
maxBitterState<-as.character(maxBitterRow$State)
maxBitterState
```

## Summary statistics for ABV (Alcohol by volume) variable.
```{r}
summary(beerBrewery$ABV)
```

##  Scatter plot to identify relationship between the bitterness of the beer and its alcoholic content
```{r Scatter}
ggplot(data=na.omit(beerBrewery),aes(x=IBU,y=ABV))+geom_point(size=1.5,alpha=.8)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
