---
title: "CaseStudy01"
author: "Rangaswamy Nagarajan"
date: "June 30, 2017"
output: 
  html_document:
    keep_md: true
---

## Beer

Beer is the world's oldest and most widely consumed alcoholic drink. It is the third most popular drink overall, after water and tea.<br />
This case study is about the analysis of data collected about Beers and Breweries in the United States of America. The data set contains a list of 2,410 US beers and 557 US breweries. 51 States are represented in the datasets.

Breweries dataset contains the list of all the breweries by City and Statewise in the USA.
It also contains the Name of the brewery and an ID for the brewery.

Beers dataset contains a list of beers available in USA.
The details that are avaialble in the dataset are Name, Beer ID, Brewery ID, Alcohol by Volume(ABV), International Bitterness Unit(IBU), Style and Ounces.
Based on the Brewery ID information we can tie the data back to the Brewery data and identify where a particular Beer was brewed.<br />

####Common glossary terms used for the data sets.<br />
####<br />Beers.csv:<br />
Name: Name of the beer.<br />
Beer ID: Unique identifier of the beer.<br />
ABV: Alcohol by volume of the beer.<br />
IBU: International Bitterness Units of the beer.<br />
Brewery ID: Brewery id associated with the beer.<br />
Style: Style of the beer.<br />
Ounces: Ounces of beer.

####<br />Breweries.csv:<br />
Brew ID: Unique identifier of the brewery.<br />
Name: Name of the brewery.<br />
City: City where the brewery is located.<br />
State: State where the brewery is located.<br />


```{r setup, results='hide'}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
getwd()
setwd("C:/Users/swara/OneDrive/Documents/MSDS/Data Science/CaseStudy/MSDSCaseStudy01/Analysis")
```




```{r, results='hide'}
beers <- read.csv("C:/Users/swara/OneDrive/Documents/MSDS/Data Science/CaseStudy/MSDSCaseStudy01/Data/Beers.csv",header=TRUE)
breweries <- read.csv("C:/Users/swara/OneDrive/Documents/MSDS/Data Science/CaseStudy/MSDSCaseStudy01/Data/Breweries.csv", header=TRUE)

names(beers)[1] <- paste("Beer_Name")
names(breweries)[2] <- paste("Brewery_Name")
```


## Below is the number of breweries in each State.
<!-- Below code is used to identify the number of breweries in each state.-->
```{r}
NoOfBreweriesPerState <- data.frame(table(breweries$State))
names(NoOfBreweriesPerState)[1]<-paste("State")
names(NoOfBreweriesPerState)[2]<-paste("Count")
NoOfBreweriesPerState
```

## Merged Beers and Breweries data.
```{r}
beerBrewery<-merge(breweries, beers, by.x="Brew_ID", by.y="Brewery_id", all=TRUE)
head(beerBrewery)
tail(beerBrewery)
```

## Below is the number of NA's in each column.
Only 3 columns have NA values.<br />
  1. ABV column has 62 NA's.<br />
  2. IBU column has 1005 NA's.<br />
  3. Style column has 5 NA's.<br />

<!--The below code is used to identify "" and replcae it with NA. There were 5 observations with style as "". the below code is used to replace "" with NA --> 

```{r}
beerBrewery$Style<-ifelse(beerBrewery[,9]=="", NA, beerBrewery[,9])
```
<!--The below code is used to count the number of NA is each column. -->
```{r}
na_count <-sapply(beerBrewery, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```


## Median alcohol content for each state.
```{r}
MedABVByState <- aggregate(ABV~State, FUN = median, beerBrewery, na.rm = TRUE)
```

## Bar chart for median alcohol content by each state.

```{r MedABVPlot, fig.width=12, fig.height=8}
ggplot(MedABVByState, aes(x=State, y=ABV, fill=ABV))+
  geom_bar(stat="identity")+
  ylab("Median Alcohol Cotent")+
  ggtitle("Medain Alcohol Content by State")+
  theme(plot.title = element_text(hjust = 0.5, size = 12, face="bold"))+
  theme(axis.text = element_text(size = 8, face="bold"))+
  theme(axis.title = element_text(size = 10, face="bold"))+
  scale_fill_gradient(low="#FF9999",high="#000099")

```


## Median international bitterness unit for each state.
```{r}
MedIBUByState <- aggregate(IBU~State, FUN = median, beerBrewery, na.rm = TRUE)
```

## Bar chart for median international bitterness unit by each state.
```{r MedIBUPlot, fig.width=12, fig.height=8}
ggplot(MedIBUByState, aes(x=State, y=IBU, fill=IBU))+
  geom_bar(stat="identity")+
  ylab("Median International Bitterness Unit")+
  ggtitle("Medain International Bitterness Unit by State")+
  theme(plot.title = element_text(hjust = 0.5, size = 12, face="bold"))+
  theme(axis.text = element_text(size = 8, face="bold"))+
  theme(axis.title = element_text(size = 10, face="bold"))+
  scale_fill_gradient(low="#FF9999",high="#000099")
```
<!-- the codes for most alcoholic beer and most biiter beer works as following.-->
<!-- first the data is sorted in descending order based on ABV/IBU column.-->
<!-- the first observation is picked up using the head function, so now we have the observation that has the maximum value.-->
<!-- the oservation is assigned to a vector and the state is output from that vector.-->
## Colorado is the state that has the most alcoholic beer.
```{r}
maxAlcoholRow<-head(beerBrewery[order(-beerBrewery$ABV),],1)
maxAlcoholState<-as.character(maxAlcoholRow$State)
maxAlcoholState
```


## Oregon is the state that has the most bitter beer.
```{r}
maxBitterRow<-head(beerBrewery[order(-beerBrewery$IBU),],1)
maxBitterState<-as.character(maxBitterRow$State)
maxBitterState
```

## Summary statistics for ABV (Alcohol by volume) variable.
```{r}
summary(beerBrewery$ABV)
```
The summary statistics show that the Minimum ABV is 0.00100, Median ABVis 0.05600 and Mean ABV is 0.05977.<br />
The Max ABV is 0.12800, which belongs to the state of Colorado that we identified in the previous question.<br />
There are also 62 NA's in the ABV data.

##  Scatter plot to identify relationship between the bitterness of the beer and its alcoholic content
```{r Scatter}
ggplot(data=na.omit(beerBrewery),aes(x=IBU,y=ABV))+geom_point(size=1.5,alpha=.8)
```

Based on the scatter plot above there seems to be some relationship between the bitterness and alcohol content of the beer.
We can clearly see from the scatter plot that as the bitterness increases the alcohol content also increased, the plot shows a positive upward movement.
